\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-16 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Starting updates in the paper ... Intro

@@

@@

>>>>

\medskip
The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient than FDM schemes when they are used to solve complex geometries. %FEM discretisation is based upon piecewise representation of the solution space and the computational domain is divided into smaller subdomains (elements) where the solution in each element is constructed from basis functions. %Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times. %At this point let us remind that a comparison of computaional methods is difficult and depends always on the test-case.
%The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to be more efficient compared with FDM schemes when they are used to solve complex geometrical domains. FEM discretization is based upon a piecewise representation of the solution in terms of specified basis functions. The computational domain is divided into smaller domains (elements) and the solution in each element is constructed from the basis functions. Advantages of FEM over FVM are the better description of the geometry and complex shapes, better treatment of fluid flow and more accurate field-solution calculations using a smaller number of nodes, less memory space and shorter run times. 
Among FEM-based formulations for porous media, the control volume finite element methods~\citep[CVFEM,][]{fung_1992} has been largely used as it can guarantee local mass conservation and high-order numerical accuracy as well as being able to use tetrahedral geometry-conforming elements. In traditional CVFEM formulations, pressure and velocity are interpolated using piecewise linear FE basis functions, %$\underline{\bf v}$ and $\underline{\bf p}$)
while material properties and flow conditions (e.g., phase saturation, density, temperature, species concentration etc) are represented with CV basis functions~\citep{voller_2009}. Saturation equations are solved explicitly after solving for the dual pressure-velocity at each non-linear iteration~\citep[a detailed description of the implicit pressure explicit saturation, IMPES, formulation can be found in][]{chen_2006,lux_2012}.

@@

Since geometries are captured by finite elements, constructed control volumes typically extend on each side of the interface which may have different properties. Therefore, some average values of the coupled velocity-pressure fields (defined in the FE space but projected into the CV space) are applied across the CVs at these interfaces. These often lead to excessive numerical dispersion especially in highly heterogeneous media (represented by spatial-dependent permeability and porosity fields). In order to overcome such artificial numerical dispersion, a discontinuous hybrid finite element finite volume method (DFEFVM) was introduced by \citet{nick_2011b, nick_2011a}. This novel discretisation scheme was designed to simulate flows through discrete fractured rocks in which CVs are divided along the interfaces of different materials. \citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}. Fluxes over CVs were calculated based upon material properties, whereas the saturation field was volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.

@@

\medskip 
In this work, a novel CVFEM formulation, previously introduced by \citet{gomes_2017}\citep[see also][]{jackson_2015,salinas2015}, is used to conduct numerical investigation of formation and evolution of viscous fingers in heterogeneous media. The continuity equation is embedded into the pressure equation to enforce mass conservation whilst ensuring force balance is preserved. A hybrid family of \PN[n]{m} triangular and tetrahedral FE pairs is used to discretise velocity and pressure, in which velocity is represented by $n$ th-order polynomials that are discontinuous across elements whereas pressure is represented by $m$ th-order polynomials that are continuous across the elements. A sketch of a \PN[1]{2} FE-pair is shown in Fig.~\ref{fig:fem_cv}a, in which velocity is represented by discontinuous and piecewise linear basis functions whereas pressure is interpolated through continuous and piecewise quadratic basis functions. Scalar fields are stored in CV space (Fig.~\ref{fig:fem_cv}b). The dual pressure and velocity fields are represented simultaneously (through non-linear projections) in FE and CV spaces.
